---
title: "MutualFunds-analysis"
author: "Sachin Sancheti"
date: "Friday, March 06, 2015"
output:
html_document:
keep_md: yes
theme: flatly
runtime: shiny
---

The document is an interactive document to help gain better insight of the scraped data from the <http://economictimes.indiatimes.com/mutual-funds>.

## Methodology
* We analyse all the funds that have performed the best over a period of time and determine the sector allocation that have performed well over that period.
* After learning on the trend, we shall decide on which sectors should be looked at favourably for investing into
* Once decided, we look at the top mutual funds with the best allocation, rank their position in terms of returns and risk to make a decision

```{r packageloading,echo=FALSE,cache=FALSE,results='hide'}
suppressPackageStartupMessages(library(dplyr))
suppressPackageStartupMessages(library(RCurl))
suppressPackageStartupMessages(library(reshape2))
suppressPackageStartupMessages(library(gdata))
suppressPackageStartupMessages(library(Hmisc))
library(tidyr)
library(stringr)
library(shiny)
suppressPackageStartupMessages(library(ggplot2))
load("alldata.RData") #dataset saved in local file after scraping
alldata[[793]]<-NULL
```

```{r integrity,echo=FALSE,results='asis',eval=FALSE}
dataintegritycheck = as.data.frame(matrix(NA,ncol=20))
for(i in 1:4234){
  dataintegritycheck = rbind(dataintegritycheck,as.data.frame(t(c(alldata[i][[1]]$smry %>% dim, alldata[i][[1]]$smry %>% dim,alldata[i][[1]]$sector %>% dim,alldata[i][[1]]$sector %>% dim,alldata[i][[1]]$fundbasics %>% dim,alldata[i][[1]]$fundbasics %>% dim,alldata[i][[1]]$manager %>%length,alldata[i][[1]]$returnsinformation %>% dim,alldata[i][[1]]$returnsinformation %>% dim,alldata[i][[1]]$url,alldata[i][[1]]$fundname,alldata[i][[1]]$i)                                                     )))
  }
dataintegritycheck <- dataintegritycheck[-1,]
# write.csv(dataintegritycheck,"dataintegritycheck.csv",quote = F)
if(apply(dataintegritycheck[,1:17],2,function(x) length(unique(x))) %>% sum ==17){
  cat("Data integrity test PASSED")
  }else{
    cat("Data integrity test FAILED")
    }
```

```{r returnsector,echo=FALSE,cache=FALSE,include=TRUE,eval=TRUE,results='hide'}
# Find funds with the highest returns
returnstable <- data.frame()
summarytable <- data.frame()
sectortable <- data.frame()
system.time(for(i in 1:4234){#length(alldata)
  returnstable <- rbind(returnstable,cbind(i = alldata[i][[1]]$i,fundname = alldata[i][[1]]$fundname,alldata[i][[1]]$returnsinformation))
  summarytable <- rbind(summarytable,cbind(i = alldata[i][[1]]$i,fundname = alldata[i][[1]]$fundname,alldata[i][[1]]$smry[c(2,4,5,7),]))
  sectortable <- rbind(sectortable,cbind(i = alldata[i][[1]]$i,fundname = alldata[i][[1]]$fundname,alldata[i][[1]]$sector))
  })
returnstable <- tbl_df(returnstable)
sectortable <- tbl_df(sectortable)
returnsectortable <- full_join(returnstable,sectortable) %>%
  mutate(Sector = ifelse(All.pc=="NA","NA",Sector))
returnsectortable[,c(4:10,12,13)] <- apply(returnsectortable[,c(4:10,12,13)],2,function(x) extract_numeric(x))
returnsectortable[,2]=as.data.frame(lapply(returnsectortable[,2],as.character),stringsAsFactors=FALSE)
apply(returnsectortable,2,class)
write.csv(returnsectortable,"returnsectortable1.csv")
```

```{r table_to_show,echo=FALSE}
inputPanel(
  selectInput("Time", label = "Sort by returns time",
              choices = (names(returnstable[4:10])), selected = "T30"),
  selectInput("Value", label = "What value of allocation would you like to see",
              choices = (names(sectortable[4:5])), selected = "All.pc")
  )

renderDataTable({
  equat <- paste("i+fundname+",input$Time,"~Sector")
  casted.returnsectortable <- dcast(returnsectortable,equat,fun.aggregate = function(x) sum(x,na.rm=TRUE),
                                    value.var = input$Value) %>%
    tbl_df
  names(casted.returnsectortable) <- make.names(names(casted.returnsectortable))
  
  sortingcols <- returnsectortable %>% tbl_df %>% rowwise() %>% mutate(Sector1 = make.names(Sector)) %>% group_by(Sector1) %>% summarise(value.invested = sum(All.value,na.rm = TRUE)) %>%
  ungroup %>%
    arrange(desc(value.invested)) %>%
    select(Sector1) %>% 
    as.data.frame %>% 
    as.vector
#  sortingcols <- apply(casted.returnsectortable[,4:(dim(casted.returnsectortable)[2]-1)],2,function(x) sum(x,na.rm = TRUE))
  finalcols <- sortingcols#data.frame(sortingcols,rows = sortingcols %>% as.data.frame %>%rownames) %>% tbl_df %>%
    #arrange(desc(sortingcols)) %>% select(rows) %>%
    #as.vector
  casted.returnsectortable %>% tbl_df() %>%
    mutate_(SortingCrit = input$Time) %>% 
    arrange(desc(SortingCrit)) %>%
    select_(~i,~fundname,~SortingCrit,.dots = lapply(finalcols$Sector1,as.symbol))
  }
)

renderDataTable({
  returnsectortable %>% tbl_df %>%
    group_by(Sector) %>% summarise(funds.invested=n_distinct(fundname),value.invested = sum(All.value,na.rm = TRUE)) %>%
    ungroup %>%
    arrange(desc(value.invested))
  },options = list(pageLength = -1))

one.word <- function(word)({
  strsplit(as.character(word),split= " ")[[1]][1]
  })


renderDataTable({
  returnsectortable %>% tbl_df %>%
    rowwise() %>%
    mutate(Company = first.word(fundname)) %>%
    group_by(Company) %>%
    summarise(Total = sum(All.value,na.rm = TRUE),
              Number.of.funds = n_distinct(fundname),
              A.T7 = sum(T7,na.rm = TRUE)/sum(!is.na(T7)),
              CV.T7 = mean(T7,na.rm = TRUE)/sd(T7,na.rm = TRUE),
              A.T30 = sum(T30,na.rm = TRUE)/sum(!is.na(T30)),
              CV.T30 = mean(T30,na.rm = TRUE)/sd(T30,na.rm = TRUE),
              A.T90 = sum(T90,na.rm = TRUE)/sum(!is.na(T90)),
              CV.T90 = mean(T90,na.rm = TRUE)/sd(T90,na.rm = TRUE),
              A.T180 = sum(T180,na.rm = TRUE)/sum(!is.na(T180)),
              CV.T180 = mean(T180,na.rm = TRUE)/sd(T180,na.rm = TRUE),
              A.T360 = sum(T360,na.rm = TRUE)/sum(!is.na(T360)),
              CV.T360 = mean(T360,na.rm = TRUE)/sd(T360,na.rm = TRUE),
              A.T1080 = sum(T1080,na.rm = TRUE)/sum(!is.na(T1080)),
              CV.T1080 = mean(T1080,na.rm = TRUE)/sd(T1080,na.rm = TRUE),
              A.T7200 = sum(T7200,na.rm = TRUE)/sum(!is.na(T7200)),
              CV.T7200 = mean(T7200,na.rm = TRUE)/sd(T7200,na.rm = TRUE) %>%
                round(2)
              )
  },options = list(pageLength = -1),
callback = "function(table) {
    table.on('click.dt', 'tr', function() {
    $(this).toggleClass('selected');
    Shiny.onInputChange('rows',
    table.rows('.selected').indexes().toArray());
    });
}"
)

renderPlot({
  tt <- returnsectortable %>% tbl_df %>%
    rowwise() %>%
    mutate(Company = first.word(fundname)) %>%
    mutate_(SortingCrit = input$Time) %>%
    group_by(Company,fundname) %>%
    summarise(returns = mean(SortingCrit,na.rm = TRUE))
  rttr <- qplot(x = Company,y = returns,data = tt,geom = c("boxplot"))+ theme(axis.text.x = element_text(angle = 90, hjust = 1))+geom_text(data = aggregate(fundname~Company,tt,length),aes(label=fundname,y = -12,size = .1))+geom_text(data = aggregate(returns~Company,tt,sd),aes(label=round(returns,1),y = -6,size = .1))
})

```

