---
title: "Scaper"
author: "Sachin Sancheti"
date: "Thursday, February 19, 2015"
output: html_document
---

This document is to explain some of the workings of the scaper designed. The data source of this scaper is from the <http://economictimes.indiatimes.com/mutual-funds>

<http://rmarkdown.rstudio.com>.

Regarding mutual fund data, some of the most useful data are usually the following for any investor:
* Net Asset Values (NAV)
* Website's rankings
* Scheme Assets Under Management
*	Fund Manager Name and Profile
*	Fund House Assets Under Management	
*	Monthly Portfolios
*	Scheme Loads
*	Portfolio Turnover
*	Expense Ratio
*	Portfolio Yields
*	Benchmark Indices
*	Average Maturity / Modified Duration

When you click the **Knit** button a document will be generated that includes both content as well as the output of any embedded R code chunks within the document. You can embed an R code chunk like this:

```{r}
summary(cars)
```

You can also embed plots, for example:

```{r, echo=FALSE}
plot(cars)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
